\begin{thebibliography}{9}
    \bibitem{touch}
    The \lstinline{touch} Command Manual Page - Linux manual page. (n.d.). \href{https://man7.org/linux/man-pages/man1/touch.1.html}{https://man7.org/linux/man-pages/man1/touch.1.html}

    \bibitem{argon2}
    Argon2 - Wikipedia. (n.d.). \href{https://en.wikipedia.org/wiki/Argon2}{https://en.wikipedia.org/wiki/Argon2}

    \bibitem{hashpass}
    Safestore: \lstinline{hash_password()} - GitHub. (n.d.). \href{https://github.com/TitusVM/icr-mp-impl/blob/main/safestore/src/cryptography/mod.rs#L70}{https://github.com/TitusVM/icr-mp-impl/blob/main/safestore/src/cryptography/mod.rs}

    \bibitem{argon2docs}
    Argon2 - docs.rs. (n.d.). \href{https://docs.rs/argon2/latest/argon2/}{https://docs.rs/argon2/latest/argon2/}

    \bibitem{aesgcm}
    AES-GCM - docs.rs. (n.d.). \href{https://docs.rs/aes-gcm/latest/aes_gcm/}{https://docs.rs/aes-gcm/latest/aes\_gcm/}

    \bibitem{dryocsign}
    DRYOC Signatures - docs.rs. (n.d.). \href{https://docs.rs/dryoc/latest/dryoc/sign/index.html}{https://docs.rs/dryoc/latest/dryoc/sign/index.html}

    \bibitem{cryptobox}
    DRYOC Classic Crypto Box - docs.rs. (n.d.). \href{https://docs.rs/dryoc/latest/dryoc/classic/crypto_box/index.html}{https://docs.rs/dryoc/latest/dryoc/classic/crypto\_box/index.html}

    \bibitem{libsodium}
    libsodium - Authenticated Encryption - libsodium documentation. (n.d.). \href{https://libsodium.gitbook.io/doc/public-key_cryptography/authenticated_encryption}{https://libsodium.gitbook.io/doc/public-key\_cryptography/authenticated\_encryption}

    \bibitem{libsodiumcrypto}
    How safe are libsodium crypto boxes? - Cryptography Stack Exchange. (n.d.). \href{https://crypto.stackexchange.com/questions/52912/how-safe-are-libsodium-crypto-boxes}{https://crypto.stackexchange.com/questions/52912/how-safe-are-libsodium-crypto-boxes}

    \bibitem{securitywhitepaper}
    Security Whitepaper - Mega. (n.d.). \href{https://mega.nz/SecurityWhitepaper.pdf}{https://mega.nz/SecurityWhitepaper.pdf}
\end{thebibliography}